%% LaTeX2e class for student theses
%% thesis.tex
%% 
%% Karlsruhe Institute of Technology
%% Institute for Program Structures and Data Organization
%% Chair for Software Design and Quality (SDQ)
%%
%% Dr.-Ing. Erik Burger
%% burger@kit.edu
%%
%% Version 1.3.2, 2017-08-01

%% Available page modes: oneside, twoside
%% Available languages: english, ngerman
%% Available modes: draft, final (see README)

\documentclass[twoside, english]{sdqthesis}

\usepackage[T1]{fontenc}
\usepackage{lmodern}

%% ---------------------------------
%% | Information about the thesis  |
%% ---------------------------------

%% Name of the author
\author{Noureddine Dahmane}

%% Title (and possibly subtitle) of the thesis
\title{Adaptive Monitoring for Continuous Performance Model Integration}

%% Type of the thesis 
\thesistype{Master’s Thesis}

%% Change the institute here, ``IPD'' is default
% \myinstitute{Institute for \dots}

%% You can put a logo in the ``logos'' directory and include it here
%% instead of the SDQ logo
% \grouplogo{myfile}
%% Alternatively, you can disable the group logo
 \nogrouplogo

%% The reviewers are the professors that grade your thesis
\reviewerone{Prof. Anne Koziolek}

\reviewertwo{Prof. Ralf Reussner}

%% The advisors are PhDs or Postdocs
\advisorone{M.Sc. Manar Mazkatli}


%% Please enter the start end end time of your thesis
\editingtime{28. März 2018}{01. Oktober 2018}

\settitle

%% --------------------------------
%% | Settings for word separation |
%% --------------------------------

%% Describe separation hints here.
%% For more details, see 
%% http://en.wikibooks.org/wiki/LaTeX/Text_Formatting#Hyphenation
\hyphenation{
% me-ta-mo-del
}

%% --------------------------------
%% | Bibliography                 |
%% --------------------------------

%% Use biber instead of BibTeX, see README
\usepackage[citestyle=numeric,style=numeric,backend=biber]{biblatex}
\addbibresource{thesis.bib}

%% ====================================
%% ====================================
%% ||                                ||
%% || Beginning of the main document ||
%% ||                                ||
%% ====================================
%% ====================================
\begin{document}

%% Set PDF metadata
\setpdf

%% Set the title
\maketitle

%% The Preamble begins here
\frontmatter

\input{sections/declaration.tex}

\setcounter{page}{1}
\pagenumbering{roman}

%% ----------------
%% |   Abstract   |
%% ----------------
 
%% For theses written in English, an abstract both in English
%% and German is mandatory.
%%
%% For theses written in German, a German abstract is sufficient.
%%
%% The text is included from the following files:
%% - sections/abstract



%% ------------------------
%% |   Table of Contents  |
%% ------------------------
\tableofcontents

\listoffigures

%% -----------------
%% |   Main part   |
%% -----------------

\mainmatter
\input{sections/abstract_en.tex}}
\input{sections/introduction.tex}
\input{sections/foundations.tex}
\input{sections/thesis_statement.tex}
\input{sections/content.tex}
\input{sections/evaluation.tex}
\input{sections/relatedwork.tex}
\input{sections/conclusion.tex}


%% --------------------
%% |   Bibliography   |
%% --------------------

%% Add entry to the table of contents for the bibliography
\printbibliography[heading=bibintoc]

\begin{thebibliography}{9}


\bibitem{latexcompanion} 
Erik Burger. 
\textit{Flexible Views for View-based Model-driven Development}. 
PhD thesis. Karlsruhe, Germany: Karlsruhe Institute of Technology, July 2014.

\bibitem{latexcompanion} 
Ralf H. Reussner et al. 
\textit{Modeling and Simulating Software Architectures – The Palladio Approach}. 
Cambridge, MA: MIT Press, Oct. 2016. 408 pp.

\bibitem{latexcompanion} 
Max E. Kramer, Erik Burger, and Michael Langhammer 
\textit{View-centric engineering
with synchronized heterogeneous models}. 
In: Proceedings of the
1stWorkshop on View-Based, Aspect-Oriented and Orthographic Software Modelling.
VAO ’13. Montpellier, France: ACM, 2013, 5:1–5:6. isbn: 978-1-4503-
2070-

\bibitem{latexcompanion} 
Mazkatli Manar, and Anne Koziolek. 
\textit{Continuous Integration of Performance Model}. 
Companion of the 2018 ACM/SPEC International Conference on Performance Engineering. ACM, 2018.

\bibitem{latexcompanion} 
Michael Langhammer.  
\textit{Automated Coevolution of Source Code and Software Architecture Models}. 
PhD thesis. Karl- sruhe, Germany: Karlsruhe Institute of Technology (KIT), 2017. 259 pp.

\bibitem{latexcompanion} 
Michael Langhammer and Klaus Krogmann.  
\textit{A Co-evolution Approach for Source Code and Component-based Archi- tecture Models}. 
 In: 17. Workshop Software-Reengineering und-Evolution. Vol. 4. 2015.

\bibitem{latexcompanion} 
André van Hoorn, Jan Waller, and Wilhelm Hasselbring.  
\textit{Kieker: A Framework for Application Performance Moni- toring and Dynamic Software Analysis}. 
In: Proceedings of the 3rd ACM/SPEC International Conference on Performance Engineering. ACM, 2012.


\bibitem{latexcompanion} 
Robert Heinrich et al.  
\textit{Integrated Observation and Modeling Techniques to Support Adaptation and Evolution of Software Systems}. 
In: DFG Priority Program SPP1593, 4th Workshop. Nov. 2014.


 
\bibitem{latexcompanion} 
Gregor Kiczales et al.
\textit{Aspect-oriented programming}. 
 In: ECOOP 97—Object-oriented programming (1997)
 



\end{thebibliography}

\end{document}